A Data-Driven Framework for Neural Field Modeling

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex

\begin{document}
    \maketitle

    \section{Reviewer 1}

        We first address the reviewer's main concerns, followed by the reviewer's additional comments.

    \subsection{Main Concerns}
    It would be useful to mention the above (now below) explicitly in the introduction and try to address them in later sections of the paper.

@@

    \begin{enumerate}
        \item Do not use real data for the validation of their approach

	\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data we believe that it is important to first validate the method artificial data, where the true and estimated parameters can be compared. Given the space limitations on the article, it is not feasible to show examples using real data in this paper. Another paper demonstrating the application of the method with data recorded from a Utah array implanted in an epilepsy surgical patient is currently in preparation. In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction.}

        \item Assume that a few kernel basis functions accurately represent the actual connectivity kernel, which might not be the case when using real data;

	\emph{The examples presented in the paper use the Mexican hat connectivity kernel. The framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic (we assume isotropy of the kernel basis functions to make the simplification in equation~18) arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support. For more complex basis functions some of the analytic derivations described in the Appendix may have to be performed numerically. We have added the above statements to the methods section (after equation~13) to be more explicit in describing subtleties of the method.}

        \item Do not consider the EEG/MEG lead field when constructing their mapping between the membrane voltage and the electrophysiological data (observation function)

	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework. Amendments have been made to the Introduction, Method, and Discussion. We have primarily developed the framework for higher density intracranial measurements. We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.

	, and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
considered. This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored. In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
    \end{enumerate}

### 2010-12-30 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to response letter

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. Each connectivity basis function can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get 

>>>>

The connectivity kernel can also be decomposed as 
\begin{equation}\label{DefKernelDecomp}
	 w\left(\mathbf{r},\mathbf{r}'\right) =\boldsymbol{\psi}^\top\left(\mathbf{r},\mathbf{r}'\right) \boldsymbol{\theta},
\end{equation}
where $\boldsymbol{\psi}(\mathbf{r},\mathbf{r}')$ is a vector of Gaussian basis functions and $\boldsymbol{\theta}$ is a vector of scaling parameters. By exploiting the isotropy of the connectivity basis functions, they can be written as  
$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$. We will assume that we know the parametric form of the connectivity basis functions, where the scaling parameters $\boldsymbol{\theta}$ are unknown. 
\dean{(for reviewer 1 point 2:) Note, that although the examples presented in this paper use the Mexican hat connectivity kernel, the framework is also valid for other connectivity kernels provided they are homogeneous and that they can be approximated by a set of isotropic basis functions parametrized by a coefficient vector $\mathbf{\theta}$. The mathematical formulation does not restrict the shape of the kernel, where anisotropic arbitrary shapes can be represented. Furthermore, the kernel basis functions need not be a Gaussian shape, but can be, for example, Laplacian to describe the ``wizard hat'' connectivity or B-spline functions to describe a kernel with a more compact support.}

Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} we get 
